---
title: "EDA_Project Report 4"
author: "Stanly Wilson Palathingal"
date: "20 November 2019"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
```

Having seen the week 3 step 18 effect, it is good to compare them with some other files. So this report is making an attempt to see some features of those attended that particular 'test'. They are compared with the enrollment data set.

```{r Installation of packages, message=FALSE}
#install.packages("ProjectTemplate")
#install.packages("rmarkdown")
#install.packages("dplyr")
```

```{r Load library and create the project, message=FALSE}
library(ProjectTemplate)
library(rmarkdown)
library(dplyr)
library(ggplot2)
# create.project("EDA_Project")
```


```{r Setting of working directory and load project, include=FALSE}
load.project()
```

The required files are loaded.
```{r loading the step activity data set}
step_act_7= read.csv("data/cyber-security-7_step-activity.csv")
step_act_6= read.csv("data/cyber-security-6_step-activity.csv")
step_act_5= read.csv("data/cyber-security-5_step-activity.csv")
step_act_4= read.csv("data/cyber-security-4_step-activity.csv")
step_act_3= read.csv("data/cyber-security-3_step-activity.csv")
step_act_2= read.csv("data/cyber-security-2_step-activity.csv")
step_act_1= read.csv("data/cyber-security-1_step-activity.csv")
```


```{r}
enrollment_7= read.csv("data/cyber-security-7_enrolments.csv")
enrollment_6= read.csv("data/cyber-security-6_enrolments.csv")
enrollment_5= read.csv("data/cyber-security-5_enrolments.csv")
enrollment_4= read.csv("data/cyber-security-4_enrolments.csv")
enrollment_3= read.csv("data/cyber-security-3_enrolments.csv")
enrollment_2= read.csv("data/cyber-security-2_enrolments.csv")
enrollment_1= read.csv("data/cyber-security-1_enrolments.csv")
```

Here the week 3 step 18 learners are separated with their id and they are inner joined with that f the enrollment file. 
```{r step_act_7,fig.height=4,fig.width=10, message=FALSE,warnings = FALSE,echo = TRUE}
step_7_1=step_act_7 %>% select(learner_id) %>% filter(step_act_7$week_number==3 & step_act_7$step_number==18)
new_7 = inner_join(enrollment_7,step_7_1,by = "learner_id")

step_6_1=step_act_6 %>% select(learner_id) %>% filter(step_act_6$week_number==3 & step_act_6$step_number==18)
new_6 = inner_join(enrollment_6,step_6_1,by = "learner_id")

step_5_1=step_act_5 %>% select(learner_id) %>% filter(step_act_5$week_number==3 & step_act_5$step_number==18)
new_5 = inner_join(enrollment_5,step_5_1,by = "learner_id")

step_4_1=step_act_4 %>% select(learner_id) %>% filter(step_act_4$week_number==3 & step_act_4$step_number==18)
new_4 = inner_join(enrollment_4,step_4_1,by = "learner_id")

step_3_1=step_act_3 %>% select(learner_id) %>% filter(step_act_3$week_number==3 & step_act_3$step_number==18)
new_3 = inner_join(enrollment_3,step_3_1,by = "learner_id")

step_2_1=step_act_2 %>% select(learner_id) %>% filter(step_act_2$week_number==3 & step_act_2$step_number==18)
new_2 = inner_join(enrollment_2,step_2_1,by = "learner_id")

step_1_1=step_act_1 %>% select(learner_id) %>% filter(step_act_1$week_number==3 & step_act_1$step_number==18)
new_1 = inner_join(enrollment_1,step_1_1,by = "learner_id")

a= bind_rows(new_1,new_2,new_3,new_4,new_5,new_6,new_7)
```

Though there are many fields in enrollment file, most of them do not have valid values. So the graph is plotted with the role of the candidate. It is seen that majority are learners and only very few are organizational admins.

```{r,fig.width=10, fig.height=7}
ggplot(new_7, aes(x="", y=role, fill=role)) +   
  geom_bar(stat="identity", width=1) + 
  coord_polar("y", start=0)+xlab("")+ylab("")
```

